PANNEURO_CFS_cleaning_WHO_pres

### 2020-11-09 PANCHANGE_data_preprocessing2020-07-15.Rmd

# Specify cohort
```{r Specify cohort}
GLAD = FALSE
EDGI = FALSE
NBR = FALSE
RAMP = TRUE
```

@@

@@

>>>>

# Specify cohort
```{r Specify cohort}
GLAD = TRUE
EDGI = TRUE
NBR = FALSE
RAMP = FALSE
GLAD_and_EDGI = TRUE
```

@@

## GLAD and EDGI
### Create data frame 
```{r GLAD and EDGI combined}
glad.and.edgi.dem.raw.id <- rbind(glad.dem.raw.id, edgi.dem.raw.id)
```

```{r glad and edgi copy dem}
if(GLAD_and_EDGI == TRUE){
  dem.raw.id <- glad.and.edgi.dem.raw.id
}
```

### Get summary of combined GLAD and EDI
```{r glad and edgi demographics summary}
if(GLAD_and_EDGI == TRUE) {
summarytools::dfSummary(
  dem.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
}
```

@@

```{r ethnicity recoding for GLAD and EDGI combined}
if(GLAD_and_EDGI == TRUE) {

### 2020-11-09 PANNEURO_analysis_WHO_pres.Rmd

---
title: "PANNEURO_analysis"
author: "Christopher Huebel, Alish Palmos, Molly Davies, and Laura Hegemann"
date: "Sys.Date()"
output:
  html_document:
    df_print: paged
    highlight: monochrome
    number_sections: no
    theme: cerulean
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: no
  pdf_document:
    toc: yes
    toc_depth: '2'
  word_document:
    toc: yes
    toc_depth: '2'
html_notebook:
  theme: cerulean
code_folding: show
toc: yes
---

@@

## Smoking

>>>>

---
title: "PANNEURO_analysis"
author: "Christopher Huebel, Alish Palmos, Molly Davies, and Laura Hegemann"
date: "Sys.Date()"
output:
  html_document:
    df_print: paged
    highlight: monochrome
    number_sections: no
    theme: cerulean
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: no

  word_document:
    toc: yes
    toc_depth: '2'
  pdf_document:

    toc: yes
    toc_depth: '2'
html_notebook:
  theme: cerulean
code_folding: show
toc: yes
---

@@

### 2020-11-09 PANNEURO_preprocessing_BMI_WHO-pres.Rmd

@@

@@

@@

nbr.bmi.raw$cm_whole <- nbr.bmi.raw$cm_all/100
nbr.bmi.raw$bmi <- nbr.bmi.raw$kg_all / (nbr.bmi.raw$cm_whole^2)
nbr.bmi.raw$bmi_new <- round(nbr.bmi.raw$bmi, digits = 2)
nbr.bmi.raw$bmi <- nbr.bmi.raw$bmi_new

>>>>

nbr.bmi.raw$Sample <- c("NBR")

nbr.bmi.raw$height.2[ nbr.bmi.raw$height.2>300 ] <- NA
nbr.bmi.raw$height.2[ nbr.bmi.raw$height.2<20 ] <- NA
nbr.bmi.raw$height.1[ nbr.bmi.raw$height.1>15 ] <- NA
nbr.bmi.raw$height.1[ nbr.bmi.raw$height.1<0.1 ] <- NA
nbr.bmi.raw$height[ nbr.bmi.raw$height>15 ] <- NA
nbr.bmi.raw$height[ nbr.bmi.raw$height<0.1 ] <- NA

@@

glad.bmi.raw$height[ glad.bmi.raw$height>300 ] <- NA
glad.bmi.raw$height[ glad.bmi.raw$height<20 ] <- NA
glad.bmi.raw$height.1[ glad.bmi.raw$height.1>15 ] <- NA
glad.bmi.raw$height.1[ glad.bmi.raw$height.1<0.1 ] <- NA
glad.bmi.raw$height.2[ glad.bmi.raw$height.2>15 ] <- NA
glad.bmi.raw$height.2[ glad.bmi.raw$height.2<0.1 ] <- NA

@@

edgi.bmi.raw$height.2[ edgi.bmi.raw$height.2>300 ] <- NA
edgi.bmi.raw$height.2[ edgi.bmi.raw$height.2<20 ] <- NA
edgi.bmi.raw$height.1[ edgi.bmi.raw$height.1>15 ] <- NA
edgi.bmi.raw$height.1[ edgi.bmi.raw$height.1<0.1 ] <- NA
edgi.bmi.raw$height[ edgi.bmi.raw$height>15 ] <- NA
edgi.bmi.raw$height[ edgi.bmi.raw$height<0.1 ] <- NA

@@

nbr.bmi.raw$cm_whole <- nbr.bmi.raw$cm_all/100
nbr.bmi.raw$bmi <- nbr.bmi.raw$kg_all / (nbr.bmi.raw$cm_whole^2)
